Searching 21-cm Absorption Systems in Chinese Radio Telescopes

### 2016-11-18 ms_21cm.tex
introduction

\newcommand{\diff}{{\rm d}}
\newcommand{\cpm}{{\small CUBEP$^3$M}}
\newcommand{\smjustify}{\hspace{-0.1cm}}
\def\smwidth{0.48\textwidth}
\def\smhwidth{0.48\textwidth}

@@

\abstract{
Neutral hydrogen clouds are known to exist in the Universe, however their spatial
distributions and physical properties are poorly understood. Such missing information
can be studied by the Chinese new generation radio telescopes by a blind searching
of 21-cm absorption systems. We forecast the abilities of surveys of 21-cm absorption
systems by two representative radio telescopes --
Five-hundred-meter Aperture Spherical radio Telescope (FAST) and
Tianlai. The result shows that, in a few of years term,
these telescopes with either high sensitivity (FAST)
or wide field of view (Tianlai) can discover orders of magnitudes
more 21-cm absorption systems, than the cumulative discoveries
in the past 50 years. 
\keywords{}
}

@@

\section{Introduction}
21-cm absorption systems can be used to directly measure the cosmic acceleration
via Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.
The current best constraint of this acceleration if given by 
\cite{2012ApJ...761L..26D}. A proposal
on CHIME-like telescope is given by \cite{2014PhRvL.113d1303Y},
in which the minor redshift drift could be measured over decades.
The uncertainties are from the poorly understood neutral hydrogen
clouds. Path finder surveys, taking less than a year, are needed
to improve our understandings of spatial distribution and physical
properties of neutral hydrogen clouds.
This can be done by the Chinese new generation radio telescopes --
Five-hundred-meter Aperture Spherical radio Telescope (FAST)
\citep{2016RaSc...51.1060L} and
Tianlai \citep{2012IJMPS..12..256C}.

\section{Sensitivity}

@@

\section{FAST estimation}

@@

\section{Tianlai estimation}

@@

\section{Conclusion}

>>>>

\newcommand{\diff}{{\rm d}}
\newcommand{\cpm}{{\small CUBEP$^3$M}}
\newcommand{\smjustify}{\hspace{-0.1cm}}
\newcommand{\HI}{{H{\small\,I}}}
\def\smwidth{0.48\textwidth}
\def\smhwidth{0.48\textwidth}

@@

\abstract{
Neutral hydrogen clouds are known to exist in the Universe, however their spatial
distributions and physical properties are poorly understood. Such missing information
can be studied by the Chinese new generation radio telescopes by a blind searching
of 21-cm absorption systems. We forecast the abilities of surveys of 21-cm absorption
systems by two representative radio telescopes in China --
Five-hundred-meter Aperture Spherical radio Telescope (FAST) and
Tianlai. The result shows that, in a few of years term,
these telescopes with either high sensitivity (FAST)
or wide field of view (Tianlai) can discover orders of magnitudes
more 21-cm absorption systems, than the cumulative discoveries
in the past 50 years. 
\keywords{}
}

@@

\section{Introduction}\label{sec.introduction}
Neutral hydrogen (\HI) clouds are known to exist in the Universe,
however only few of them are discovered in the past half a century,
and we poorly understand their spatial distribution and physical
properties \citep{2005ARA&A..43..861W}. 
In damped Lyman-$\alpha$ absorption (DLA)
systems, the radio spectrum is also substantially absorbed by the {\HI}
hyperfine structure, whose rest frame wavelength is approximately 21 cm
($\sim$1420 MHz in frequency). These systems are defined to have
at least $2\times 10^{20}$ cm$^{-2}$ {\HI} column density, thus being
able to house cold 21-cm absorbing gas in the cold neutral medium (CNM).

The 21-cm absorption systems are important in the study of the 
distribution, location, temperature and structure of neutral gas,
and the evolution of neutral gas systems and galaxies over
cosmic time scale.
Due to the narrow intrinsic line width, the 21-cm absorption systems
are proposed to be used to directly measure the cosmic acceleration
\citep{2012ApJ...761L..26D,2014PhRvL.113d1303Y}, via the 
Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.
The uncertainties are from the poorly understood neutral hydrogen
clouds. Path finder surveys, taking less than a year, are needed
to improve our understandings of spatial distribution and physical
properties of neutral hydrogen clouds.
This can be done by the Chinese new generation radio telescopes --
Five-hundred-meter Aperture Spherical radio Telescope (FAST)
\citep{2016RaSc...51.1060L} and
Tianlai \citep{2012IJMPS..12..256C}. In the current and near future,
these are the two symbolic modern radio telescopes in China.
The single-dish FAST, like Arecibo\footnote{https://www.naic.edu},
uses its gigantic single dish to achieve ultimate sensitivity, whereas
Tianlai, designed like CHIME\footnote{http://chime.phas.ubc.ca},
has ultra wide field of view per day, by
using its cylindrical reflectors and arrays of receivers to
scan the northern hemisphere of the sky as the Earth turns.

According to their different design and observing strategies,
we forecast their abilities of blind searching of 21-cm absorption
systems. In section \ref{sec.sensitivity} we show the sensitivity
estimation and all the aspects
needed to be taken into account,
and according to the configurations of FAST and Tianlai,
we show their forecast in section \ref{sec.FAST}
and section \ref{sec.Tianlai} respectively.
Conclusions are made in section \ref{sec.conclusion}.

\section{Sensitivity}\label{sec.sensitivity}

@@

\section{FAST estimation}\label{sec.FAST}

@@

\section{Tianlai estimation}\label{sec.Tianlai}

@@

\section{Conclusion}\label{sec.conclusion}
